Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-20 disc.tex
[draft]numerical results revision 1

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the echo is always $\frac{1}{4} \ln t$, regardless of the theta angle. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two corresponds to the parts of the Lorentz group and can't be connected by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of $DD \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
\end{equation}
which gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation. This is very likely due to the ambiguity of the free boson zero mode, as moving slight way from the point remedy the situation. And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation. Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy. It would be interesting to have a CFT calculation to reproduce the better numerical result of
\begin{equation}
{\rm ND} + {\rm DN} \rightarrow \lambda + {\rm ND} 
\end{equation}

>>>>

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the echo is always $\frac{1}{4} \ln t$, regardless of the theta angle. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two corresponds to the parts of the Lorentz group and can't be connected by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
\end{equation}
which gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation. This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation. And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation. Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy. It would be interesting to have a CFT calculation to reproduce the better numerical result of
\begin{equation}
{\rm ND} + {\rm DN} \rightarrow \lambda + {\rm ND} 
\end{equation}

\todo[inline]{insert the ND + DN figure. Compare it with the DN + DN figure}

### 2017-05-20 num_result.tex
[draft]numerical results revision 1

In order to check our analytic results, we reconsider the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice}. In particular, we calculate the Loschmidt echo and bipartite fidelity for various joining boundary conditions determined by $S_1(\theta)$ or $S_2(\theta)$. We refer the reader to App.~\ref{app:comp_fid_echo} for the technical details.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The slope of the free energy for Loschmidt echo in the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$ where $\theta\in(0,\frac{\pi}{2})$. We work with total system size $N=30k$ sites, with parameters $m=10^{-8}$,$k=1$. The lattice constant is set to unity. The blue dots are the numerical results and the red line is the analytical result. As predicted, the slopes are equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta=0.02\pi$ shown in log scale. The dashline denotes the power law with $t^{-0.25}$. The curve fitting method is described in the main text.}
\label{fig:DDDD}
\end{figure}

We start with the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$ and the numerical simulation is performed for $\theta=0.02n\pi$, $n=1,...,25$. The results for Loschmidt echo is shown in Fig.~\ref{fig:DDDD}, and numerical parameters are given in the caption. The green dots correspond to numerical results for the slope of free energy, and the solid line shows the analytical result for echo in Eq.~\eqref{eq:result_DDDD}. The inset shows the double logarithmic plot of Loschmidt echo versus time for the case $\theta=0.02\pi$. The dashline denotes the expected power law decay $\mathcal{L}(t)\sim t^{-0.25}$. For the curve fitting, we randomly pick a data point near $t=10$ and fit the lower half of the data. This is repeated five times and we calculate the mean and standard deviation for the exponents. With the data processing method described, the error bar in the main figure is invisible on the data points. We have performed the identical simulation for the process $\text{NN}+\text{NN}\rightarrow\lambda+\text{NN}$ and obtained identical result shown in Fig.~\ref{fig:DDDD} (the initial decay of Loschmidt is different but has the same exponent at larger time). We note one caveat for this case with Neumann boundary conditions on both sides of the chain. Because of the zero mode, it is expected (indeed we saw) that the numerical simulation may not be stable. The problem can be avoided by adding a small mass regulator $m=10^{-8}$. Similar numerical analysis can be applied to calculate the fidelity which matches the result in Eq.~\eqref{eq:result_DDDD}. We shall not show the result here.

Next we analyze the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ in which the joining boundary condition is determined by $S_1(\theta)$. There is one subtly which is that $S_1(0)$ corresponds to `DN' and the process reduces to $\text{DN}+\text{DN}\rightarrow\text{DN}+\text{DN}$. The zero mode will cause the numerical simulation unstable near $\theta=0$, and it turns out that the mass regulator cannot resolve this problem. Rather, we shall shift one of the `DN' slightly and consider the following process
\begin{eqnarray}\begin{aligned}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
\end{aligned}\end{eqnarray}
where we take $\delta\theta=0.003\pi$ and $\theta=0.02n\pi$, $n=1,...,25$. We shall discuss the introduction of extra bcc at $-\infty$ due to this shift in Sec.~\ref{sec:disc}. We show the numerical result for Loschmidt echo in Fig.~\ref{fig:DDNN}(a). The slope of the free energy follows a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. The deviation from the analytic result (without the shift) near $\theta=0$ has been greatly suppressed because of $\delta\theta$ introduced manually. The numerical results near $\theta=0.5\pi$ will match the analytical ones more precisely if we were to set $\delta\theta=0$.

Next we perform the numerical simulation for $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ with $\theta\in(0,\frac{\pi}{2})$.  We recall that

{\color{red}say why echo bad, say we shift it that is why dot below curve slightly near pi, say there is extra bcc, say why fidelity better, say to confirm we do fidelity as shown in Fig.~\ref{fig:DDNN}(b) and it is good, confirm our conjecture. }

We further consider the case $\text{P}+\text{P}\rightarrow\lambda+\text{P}$, and the numerical results for Loschmidt echo and fidelity are shown in Fig.~\ref{fig:PPPP}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DN_DN2tan.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=30k$ sites with the same parameters in Fig.~\ref{fig:DDDD}. The numerical value of slopes follow a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. For the deviation from the analytic results in (a), see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
    \todo[inline]{Tianci: make the plots have the same style?}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
    \caption{daf}
    \label{fig:PPPP}
    \todo[inline]{Mao: Put the PPPP for echo; Tianci: make the plots have the same style?}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$. We work with total system size $N = 30k$ sites, and parameters $m = 10^{-8}$, $k = 1$. The lattice constant is set to unity. The blue dots representing the numerical results lie on the red analytic line. As predicted, the echo exponents are equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale. The dashline denotes the expected power law of $t^{-0.25}$. The finite size effect do not emerge before $t=10^{3}$, which sets the right boundary of the range we fit. See main text for the curve fitting method.}
\label{fig:DDDD}
\end{figure}

We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results. Our numerical evaluations is based on Boson Bogoliubov transformation and explicit form of the groundstates. The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details. In all the figures, we present the coefficients of the logarithmic term $\mathcal{F} / \ln L$ and $\mathcal{F} / \ln t$ and call them fidelity and echo exponents respectively.

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}
\end{equation}
and shows its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as a dashline for comparison. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $. To avoid subjective choice of data points, we repeat 5 times to randomly pick {\color{red} 10 points} before the finite size revival surges to obtain the deviation. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

We also calculate the companion process
\begin{equation}
 \text{NN}+\text{NN}\rightarrow\lambda+\text{NN}
\end{equation}
and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}. The avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$. While the short time decay pattern are different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity. We therefore do not present the result here.

Next we analyze the more interesting $\theta$ dependent process
\begin{equation}
  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN}
\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $\mathcal{S}_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This "shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DN_DN2tan.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi, 0.24\pi$ and $0.48\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
    \todo[inline]{Tianci: make the plots have the same style?}
\end{figure}

We finally consider the case
\begin{equation}
\text{P}+\text{P}\rightarrow\lambda+\text{P}
\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occur at $\theta \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_DNDN}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right)
\end{aligned}
\end{equation}
where we take $\theta=0.003\pi$. The $\theta$ dependent exponents now is a shifted quadratic curve symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
    \todo[inline]{Mao: Put the PPPP for echo; Tianci: make the plots have the same style?}
\end{figure}

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:
